\sektion{4}{Conclusion}

\subsection{Evaluation}

The result is a webapp that meets my goal and guiding design philosophies:
\numlist
    \item \textbf{Intelligent registration and data collection:} Achieved through the Resource Scraper and Transcript Parser modules. Registration should take no more than 2-3 minutes, and should not discourage students from using the app at all.
    \item \textbf{Painless application and hiring processes:} On the resource side, application is reduced to selecting which courses you are interested in; more work is only required when advanced to a second round. On the manager side, hiring decisions are performed through a point and click interface, with systems in place for requesting and reviewing further information.
    \item \textbf{Powerful and intuitive management tools:} Management is done largely through sortable and searchable tables with clear purposes and functions.
    \item \textbf{RESTful API:} Successfully constructed and documented.
    \item \textbf{Extensible Code Design:} Code was written modularly and as loosely coupled as possible to support future feature implementations.
\finnumlist

\subsection{Future Work}

This system is still in development, and is flexible enough to be extended in several aspects.

We plan to eventually integrate with other apps, which allows the system to collect more useful data and provide more powerful features. For example, we could connect with codePost, and track average number of comments per grader, which would allow us to match students who desire more feedback with the appropriate graders. We could also link with the Time Collection system, to automatically record and display work hours. We also plan to introduce data analyzing algorithms, which opens the door for autonomous performance evaluation, and advanced management scouting features. There is even the potential for generalizing the app, and marketing it to other interested universities. The possibilities are endless.

The current plan is to have the COS 126 Grading team use the system for hiring next semester, which will give us real data and user feedback to respond to. From there, we will expand to the rest of the department and beyond.

\subsection{Closing Thoughts}

We believe this app will be of tremendous use to the university. For the immediate future, the product will allow the COS department to be more liberal in hiring undergraduate workers, and will allow more students to get relevant work experience on campus. Eventually, we hope the system will be able to permeate and benefit other departments and universities as well.

\subsection{Acknowledgments}

I'd like to thank \advisor{} for his advice and creative ideas throughout the project. I'd also like to thank Benjamin Parks, who provided the base implementation of the college facebook scraper.
