\documentclass[../report.tex]{subfiles}
\begin{document}

\pagebreak
% Don't display section title
\begingroup
\renewcommand{\section}[2]{}

% Remove Justification and singlespace
\begin{singlespace}
\begin{flushleft}

% Set font size
\begin{footnotesize}

% Actual Bibliography
\begin{thebibliography}{\kern\bibindent}

    \bibitem{greenstreet}
        Christoph Kern, Mark R. Greenstreet, Formal verification in hardware design: a survey, ACM Transactions on Design Automation of Electronic Systems (TODAES), v.4 n.2, p.123-193, April 1999 
    \bibitem{validating-sat}
        L. Zhang and S. Malik, “Validating sat solvers using an independent resolution-based checker: Practical implementations and other applications,” in Proceedings of the conference on Design, Automation and Test in Europe-Volume 1, p. 10880, IEEE Computer Society, 2003.

    \bibitem{z3-smt-solver}
        de Moura L., Bjørner N. (2008) Z3: An Efficient SMT Solver. In: Ramakrishnan C.R., Rehof J. (eds) Tools and Algorithms for the Construction and Analysis of Systems. TACAS 2008. Lecture Notes in Computer Science, vol 4963. Springer, Berlin, Heidelberg

    \bibitem{hardware-accel}
        R. Weber, A. Gothandaraman, R. J. Hinde and G. D. Peterson, "Comparing Hardware Accelerators in Scientific Applications: A Case Study," in IEEE Transactions on Parallel and Distributed Systems, vol. 22, no. 1, pp. 58-68, Jan. 2011.

    \bibitem{ila}
        S. Malik and S. Subramanyan, "Specification and Modeling for Systems-on-Chip Security Verification"
        % TODO: Fix both of these
    \bibitem{ila-template}
        P. Subramanyan,  Y. Vizel, et-al "Template-based Synthesis of
        Instruction Level Abstractions for SoC Verification"

    \bibitem{elane}
E. Chou and S. Malik, "A Secure Bootloader for Demonstrating Formal Verification of Hardware-Firmware Interactions on SoCs"

    \bibitem{security-basics}
        Lee, Ruby B. "Security basics for computer architects." Synthesis Lectures on Computer Architecture 8.4 (2013): 1-111.

    \bibitem{secure-bootloader}
        Cammack, William E., and Jason Douglas Kridner. "Secure bootloader for securing digital devices." U.S. Patent No. 7,237,121. 26 Jun. 2007.
    \bibitem{fw-summit}
        ``Chrome OS Firmware Overview'' Google Inc. Accessed November 1, 2016. \url{https://docs.google.com/presentation/d/1h-nsDGlQmYI21dr95nYgLmyCYDgBIpJWSt9b7AqTZaw/pub?start=false&loop=false&delayms=3000&slide=id.g2ba203e62_048}        

    \bibitem{TPM}
        ``Trusted Platform Module'' Trusted Computing Group.\url{https://trustedcomputinggroup.org//work-groups/trusted-platform-module/}
    \bibitem{TCG}
        Trusted Computing Group. \url{http://www.trustedcomputinggroup.org.}
    \bibitem{git}
        ``Git. Fast version Control'' Accessed December 10, 2016. \url{https://git-scm.com/}

    \bibitem{vboot-design-doc}
    ``Firmware Boot and Recovery'' Google Inc. Accessed November 1, 2016. \url{http://www.chromium.org/chromium-os/chromiumos-design-docs/firmware-boot-and-recovery}

\bibitem{repo}
    ``Developing with Git and Repo'' Google Inc. Accessed January 2, 2017. \url{http://source.android.com/source/developing.html}

\bibitem{coreboot}
    ``Coreboot'' Accessed November 3, 2016. \url{https://www.coreboot.org/}

\bibitem{my-repo}
    ``Coreboot'' Accessed March 6, 2017. \url{https://github.com/gilhooleyd/CBMC-Vboot}

\bibitem{coreboot-payload}
    ``Acquiring, Building, and Configuring the Payload Compatible with the Coreboot Reference Bootloader'' Intel. December 2015 \url{http://www.intel.com/content/dam/www/public/us/en/documents/white-papers/coreboot-reference-bootloader-white-paper.pdf}

\bibitem{depthcharge-slides}
    ``Depthcharge: The ChromeOS bootloader'' Google Inc. Accessed November 3, 2016.
    \url{https://a77db9aa-a-7b23c8ea-s-sites.googlegroups.com/a/chromium.org/dev/chromium-os/2014-firmware-summit/ChromeOS\%20firmware\%20summit\%20-\%20Depthcharge.pdf?attachauth=ANoY7crD3ii0STwDVZHwBB0OCdcPXkiczTeo9TaIDJ4pntDcLPqwiA_zHy98OVs_SgenmBV5c-1HcuyT50zByhY0Y5qngp9ju8ziU74J6OMh3xPpPsqpBVLlDsCu57BSzIKvB4XZ9MLlDAZXMO8NaIRRwTIsaj1gtreX072tvLDYAIh6V8GpR542uMiV4YpOAbR0oJ64X4g60lUFoIHGTEMbhPRe-CQZJT6nlJyjsH_iPRrntmN_OtJtJRI7KmDd5zMeopwIbupHKCaUW24wQF_4KudBJ7oLp6s01cjknwyW-wY9op-M8Wg\%3D&attredirects=1}
\bibitem{depthcharge-codebase}
    ``Depthcharge Codebase'' Google Inc. \url{https://chromium.googlesource.com/chromiumos/platform/depthcharge/}

\bibitem{vboot-codebase}
    ``Verified Boot CodeBase'' Google Inc. \url{https://chromium.googlesource.com/chromiumos/platform/vboot_reference/}

\bibitem{developer-mode}
    ``Chrome OS Developer Mode'' Google Inc. \url{http://www.chromium.org/chromium-os/chromiumos-design-docs/developer-mode}

\bibitem{vboot-data-structures}
    ``Verified Boot Data Structures'' Google Inc. \url{http://www.chromium.org/chromium-os/chromiumos-design-docs/verified-boot-data-structures}

\bibitem{minisat}
    Sorensson, Niklas, and Niklas Een. "Minisat v1. 13-a sat solver with conflict-clause minimization." SAT 2005 (2005): 53.
\bibitem{my-repo}
    D. Gilhooley. \url{https://bitbucket.org/david\_gilhooley/personal-vboot}, 2017
\bibitem{tpm-book}
    Challener, David. \textit{A Practical Guide To Trusted Computing}. 1st ed. Upper Saddle River, NJ: IBM Press/Pearson plc, 2008. Print.
\bibitem{tpm-slides}
    Ng, Raymond. \textit{TPM Fundamentals}. Infineon, APTISS. 2008. Slides.
\bibitem{qemu-site}
    ``QEMU: the Fast processor emulator'' \url{http://www.qemu-project.org/}
\bibitem{TPMLibs}
    Stefan, Berger. LibTpms. \url{https://github.com/stefanberger/libtpms}
\bibitem{SWTPM}
    Stefan, Berger. SwTpm. \url{https://github.com/stefanberger/swtpm}
\bibitem{TPMQEMU}
    Stefan, Berger. Qemu-Tpm. \url{https://github.com/stefanberger/qemu-tpm}
\bibitem{multiboot}
    ``Multiboot Specification'' \url{https://www.gnu.org/software/grub/manual/multiboot/multiboot.html}
\bibitem{trustfound}
    Bai, Guangdong, et al. ``Trustfound: Towards a formal foundation for model checking trusted computing platforms.'' \textit{International Symposium on Formal Methods.} Springer International Publishing, 2014.
\bibitem{load-protocol}
    Krstic, Sava, et al. ``Security of SoC firmware load protocols.''
    \textit{Hardware-Oriented Security and Trust (HOST), 2014 IEEE International Symposium on.} IEEE, 2014.

\end{thebibliography}
\end{footnotesize}
\end{flushleft}
\end{singlespace}
\endgroup
\pagebreak
\end{document}
